### 2025-02-19 paper/paper.tex
Finished texts, graphs and tables

\documentclass[11pt,twoside,a4paper]{article}
\usepackage[hmargin=2cm, vmargin=2cm]{geometry}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{float}
\usepackage{subcaption} 
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage[hidelinks=true]{hyperref}
\usepackage{overpic}
\usepackage[font=small,skip=2pt]{caption}

@@

>>>>

\documentclass[11pt,twoside,a4paper]{article}
\usepackage[hmargin=2cm, vmargin=2cm]{geometry}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{setspace}
\usepackage{xcolor}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{float}
\usepackage{subcaption} 
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage[hidelinks=true]{hyperref}
\usepackage{overpic}
\usepackage[font=small,skip=2pt]{caption}

@@

\newpage
\subsection{Quantitative Results}

\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|c|c|}
        \hline
        Methods & Optimal components & Avg CV MSE of prediction & Dataset: Multicollinearity level \\
        \hline
        OLS & NA & 0.0106 & \multirow{3}{*}{No multicollinearity} \\
        PCR & 10 & 0.0106 &  \\
        PLS & 10 & 0.0106 &  \\
        \hline
        OLS & NA & 1.0642 & \multirow{3}{*}{Moderate} \\        
        PCR & 5 & 1.0477 &  \\
        PLS & 3 & 1.0477 &  \\
        \hline
        OLS & NA & 1.4639 & \multirow{3}{*}{Severe} \\
        PCR & 3 & 1.1452 &  \\
        PLS & 3 & 1.1492 &  \\ 
        \hline  
        OLS & NA & NA & \multirow{3}{*}{NIR spectroscopy data} \\
        PCR & 15 & 0.0898 &  \\
        PLS & 12 & 0.0849 &  \\ 
        \hline
    \end{tabular}
    \caption{Prediction accuracy and optimal components across different multicollinearity levels}
    \label{tab:multicollinearity_comparison}
\end{table}

\begin{table}[h]
    \centering
    \begin{tabular}{|c|c|c|c|c|}
        \hline
        Methods & Avg MSE of regression coefficients &  $\text{Bias}^2$ & Variance & Dataset: Multicollinearity level \\
        \hline
        OLS & 0.0001 & 0.0 & 0.0001 & \multirow{3}{*}{No multicollinearity} \\
        PCR & 0.0063 & 0.0 & 0.0063 &  \\
        PLS & 0.0001 & 0.0 & 0.0001 &  \\
        \hline
        OLS & 0.6598 & 0.0002 & 0.6596 & \multirow{3}{*}{Moderate} \\        
        PCR & 0.2414 & 0.2334 & 0.0080 &  \\
        PLS & 0.2305 & 0.2285 & 0.0020 &  \\
        \hline
        OLS & 12.7383 & 0.0072 & 12.7310 & \multirow{3}{*}{Severe} \\
        PCR & 0.5993 & 0.4221 & 0.1772 &  \\
        PLS & 0.4118 & 0.2719 & 0.1400 &  \\ 
        \hline
    \end{tabular}
    \caption{MSE coefficient decomposition across different different multicollinearity levels}
    \label{tab:Stability_analysis}
\end{table}
